Supermartingales and Termination Analysis of Statistical PCF

### 2020-06-09 relativised-completeness.tex
Comment

For 1, consider the following:
\begin{proof}
If $T$ is bounded by $b$ a.s.~(for $n$ constant), the statement is trivially true by taking $\epsilon$ to be constantly 1, and $Y_n = b - n$.
Otherwise, let $(T_n)_{n \in \omega}$ be defined recursively such that $T_0 = 0$, $T_{n+1} > T_n$ and $\mathbb P[T > T_{n+1}] \leq \frac 1 4 \mathbb P[T > T_n]$. \lo{Since $T$ is a stopping time, we can assume that $T_n \in \mathbb N$. 
Problem with $T_1$: we require $T_1 > 0$ which may contradict the requirement $\mathbb P[T < T_{1}] \leq \frac 1 4 \mathbb P[T < 0] = 0$ for certain $T$, such as those that satisfy $\mathbb P[T < 1] > 0$.
We could define $T_1$ as the least number satisfying $\mathbb P[T < T_1] \geq \frac{1}{4}$.} \akr{Sorry, I just wrote it wrong. I assume this ($\mathbb P[T > T_n]$ instead of $\mathbb P[T < T_n]$) resolves your concern.}
We will then define a supermartingale $(Y_n)_{n \in \omega}$ and nonrandom sequence $(Y'_n)_{n \in \omega}$ such that $Y_n = 0$ iff $T < n$ \changed[lo]{a.s.}, $Y_n = Y'_n$ iff $T \geq n$ \changed[lo]{a.s.}, and $Y'_n \geq 2^k$ for $n \geq T_k$.

>>>>

For 1, consider the following:
\begin{proof}
If $T$ is bounded by $b$ a.s.~(for $n$ constant), the statement is trivially true by taking $\epsilon$ to be constantly 1, and $Y_n = b - n$.
Otherwise, let $(T_n)_{n \in \omega}$ be defined recursively such that $T_0 = 0$, $T_{n+1} > T_n$ and $\mathbb P[T > T_{n+1}] \leq \frac 1 4 \mathbb P[T > T_n]$. \lo{Since $T$ is a stopping time, we can assume that $T_n \in \mathbb N$. 
Problem with $T_1$: we require $T_1 > 0$ which may contradict the requirement $\mathbb P[T < T_{1}] \leq \frac 1 4 \mathbb P[T < 0] = 0$ for certain $T$, such as those that satisfy $\mathbb P[T < 1] > 0$.
We could define $T_1$ as the least number satisfying $\mathbb P[T < T_1] \geq \frac{1}{4}$.} \akr{Sorry, I just wrote it wrong. I assume this ($\mathbb P[T > T_n]$ instead of $\mathbb P[T < T_n]$) resolves your concern.}
We will then define a supermartingale $(Y_n)_{n \in \omega}$ and nonrandom sequence $(Y'_n)_{n \in \omega}$ such that $Y_n = 0$ iff $T < n$ \changed[lo]{a.s.} \akr{I see no reason that this can't just be true everywhere, as this is part of the definition of $Y_n$. Likewise for the other ``a.s.'' you added.}, $Y_n = Y'_n$ iff $T \geq n$ \changed[lo]{a.s.}, and $Y'_n \geq 2^k$ for $n \geq T_k$.
